Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-04-03 src/docs_paper/paper.Rmd
Appendix puzzle fixes and paper edits

<!-- * [ ] Description of the ART attendance component of the model -->
<!-- * [ ] Tying together Naomi model within LGM / ELGM mathematical notation -->
<!-- * [ ] Create DAG representing Naomi model -->
<!-- * [ ] Rewrite section on why Naomi is an ELGM, drawing from slides -->
<!-- * [ ] Write section on Laplace approximation -->
<!-- * [ ] Write section on AGHQ, tying together connection to Laplace for k = 1 -->
<!-- * [ ] Move algorithm to algorithm environment -->

@@

Naomi is not an LGM, and instead falls into the ELGM class, for the following reasons:

1. In the household survey component (Section \ref{sec:household}), the HIV incidence rate depends on the HIV prevalence and ART coverage linear predictors.
2. In the ANC testing component (Section \ref{sec:anc}), the HIV prevalence and ART coverage depend upon the household survey component.
Specifically, $|\mathcal{J}_i| = 2$ such that for $\theta \in \{\rho, \alpha\}$
$$
\mu_i = g_i(\eta^\theta_i, \eta^{\theta^{\text{ANC}}}_i) = \text{logit}^{-1}(\eta^\theta_i + \eta^{\theta^{\text{ANC}}}_i).
$$
3. In the ART attendance component (Section \ref{sec:art}), the multinomial logistic regression.
4. In all components the data we model is aggregated. Processes are modelled at the finest distict-age-sex division $i$, but likelihoods are defined for observations over sets of indices $\mathcal{I}$.

<!-- To-do: define what exactly $p(\y, \x, \btheta)$ is for the Naomi model -->

@@

@@

A quadrature rule can be used to approximate the integral of a function $f: \mathcal{Z} \to \mathbb{R}$ by a weighted sum
$$
\int_{\z \in \mathcal{Z}} f(\z) \text{d}\z \approx \sum_{\z \in \mathcal{Q}} f(\z) w(\z)
$$
where $\z \in \mathcal{Q} \subset \mathcal{Z}$ are a set of nodes and $\omega: \mathcal{Q} \to \mathbb{R}$ is a weighting function.
In Gauss-Hermite quadrature [@davis1975methods] the nodes are selected as zeros of the Hermite polynomials.
These nodes and weights can be shifted and scaled to suit the particular integrand using adaptive Gauss-Hermite quadrature [@naylor1982applications; @tierney1986accurate].

>>>>

<!-- * [ ] Tying together Naomi model within LGM / ELGM mathematical notation -->
<!-- * [ ] Create DAG representing Naomi model -->
<!-- * [ ] Rewrite section on why Naomi is an ELGM, drawing from slides -->
<!-- * [ ] Write section on Laplace approximation -->
<!-- * [ ] Write section on AGHQ, tying together connection to Laplace for k = 1 -->
<!-- * [ ] Move algorithm to algorithm environment -->

@@

Naomi is not an LGM, and instead falls into the ELGM class, because:

1. In the ANC testing component (Section \ref{sec:anc}), the HIV prevalence and ART coverage depend upon the household survey component.
Specifically, $|\mathcal{J}_i| = 2$ such that for $\theta \in \{\rho, \alpha\}$
$$
\mu_i = g_i(\eta^\theta_i, \eta^{\theta^{\text{ANC}}}_i) = \text{logit}^{-1}(\eta^\theta_i + \eta^{\theta^{\text{ANC}}}_i).
$$
2. In the household survey component (Section \ref{sec:household}), the HIV incidence rate depends on adult HIV prevalence and adult ART coverage via non-linear transformations.
3. Individuals who are taking ART, or have been recently infected, must be HIV positive. As a result observations are made taking the product of HIV prevalence with ART coverge or recent HIV infection.
4. Recent HIV infection is non-linearly linked to both HIV incidence and HIV prevalence.
5. The ART attendance component (Section \ref{sec:art}) uses a multinomial model.
6. Processes are modelled at the finest distict-age-sex division $i$, but likelihoods are defined for observations aggregated over sets of indices $\mathcal{I}$.
7. Multiple link functions are used: there is no one $g$.

@@

To write.

@@

A quadrature rule can be used to approximate the integral of a function $f: \mathcal{Z} \to \mathbb{R}$ by the following weighted sum
$$
\int_{\z \in \mathcal{Z}} f(\z) \text{d}\z \approx \sum_{\z \in \mathcal{Q}} f(\z) w(\z),
$$
where $\z \in \mathcal{Q} \subset \mathcal{Z}$ are a set of nodes and $\omega: \mathcal{Q} \to \mathbb{R}$ is a weighting function.
In Gauss-Hermite quadrature [@davis1975methods] the nodes are selected as zeros of the Hermite polynomials, and weights so as to interpolate functions of the form $f(\z) = \tilde f(\z) \exp(-\z^2)$.
These nodes and weights can be shifted and scaled to suit the particular integrand using adaptive Gauss-Hermite quadrature [@naylor1982applications; @tierney1986accurate].
AGHQ with $k = 1$ recovers the Laplace approximation.
